---
title: "rFishTaxa: `Eschmeyer's Catalog of Fishes` Mining with R"
author: "Liuyong Ding\\

        Institute of International Rivers and Eco-security, Yunnan University"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{rFishTaxa introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
  %\VignetteDepends{dplyr}
  %\VignetteDepends{magrittr}
---

## Introduction

`Eschmeyer's Catalog of Fishes` \url{https://www.calacademy.org/scientists/projects/catalog-of-fishes} is the authoritative reference for taxonomic fish names, featuring a searchable on-line database. This **rFishTaxa** package helps users to obtain valid taxonomic fish information for biodiversity estimates, conservation issues, etc.


## Example

##### Load the **rFishTaxa** package

```{r}
options(warn = -1)
library("rFishTaxa")
```

##### Genera/Species of Fishes by Family/Subfamily through 2022:

```{r }

species_family()

```


##### Searching for genera in a family:

```{r }
r1 <- search_cas(query = c("cyprinidae","balitoridae"),type = "genus_family")

head(r1)

```


##### Searching for species in a family:

```{r }
r2 <- search_cas(query = "balitoridae",type = "species_family")

head(r2)
```


##### Searching for species in a genus:

```{r}
r3 <- search_cas(query = "Brachyplatystoma",type = "species_genus")

head(r3)
```


##### Searching for species related to a species or subspecies:

```{r }
r4 <- search_cas(query = c("Anguilla nebulosa", "Clupisoma sinense"),type = "species")

head(r4)

# Each matching row by family
library(magrittr)
r4 %>% dplyr::left_join(species_family()[,1:4],by = "family")

```


## Contribution

Latin-Chinese Dictionary of Fishes Names Introduction In the last 20-30 years, significant progress has been made in the work of fish. However the contents of a few published Latin-Chinese dictionaries of world's fish names are still incomplete and cannot satisfy the increasing demand by the Chinese language people for the purpose's such as research, teaching, conservation, fisheries, or aquatic trade use. 

Future versions try to add [`Lantin-Chinese Dictionary of Fish Names by Classification System`](http://www.taiwan-fisheries.com.tw/news-preface-2e.htm) to this package.


Contributions to this package are welcome. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [**an issue**](https://github.com/Otoliths/rFishTaxa/issues).
